Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-10-26 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
About volunteer issues #50
Added a paragraph about issues of volunteer systems. I only have th
BOINC site as reference, any others?

In this sense, in this paper we propose {\sf NodIO}, a cloud or metal
based 
volunteer evolutionary computing system based on the {\sf NodEO}
library, whose architecture 
has been developed using JavaScript on the client as well as the
server sides. 
All parts of the system are free and available with a free
license from \url{https://github.com/JJ/splash-volunteer}.
Thus, {\sf NodIO} architecture has two tiers:\begin{enumerate}
\item A REST server, that is, a server that includes several {\em
  routes} 
  that can be called for storing and retrieving information (the CRUD cycle:
  create, request, update and delete) from the server. The information
  is of two kinds: {\em problem} based, that is, related to the
  evolutionary algorithm such as {\tt PUT}ing a chromosome in or {\tt
    GET}ing a random chromosome from it, and {\em information} related
  to performance and state of the experiments. It also performs logging
  duties, but is basically a very lightweight and high performance
  data store \cite{jj:idc:lowcost}.
  The server has the capability to
  run a single experiment, storing the chromosomes in a data structure
  that is reset when the solution is found.
\item A client that includes the evolutionary algorithm as
  JavaScript code embedded in a web page that displays graphs and some
  additional links and information on the experiment. This code runs
  an evolutionary algorithm {\em island} starting with a random
  population and sending, every 100 generations, the best individual
  back to the server (via a {\tt PUT} request) and requesting a random
  individual from the server (via a {\tt GET} request). Apart from
  these constants, the algorithm can be run in many different ways:
  stopping when a solution is found or, as we have done in this paper,
  using Web Workers, which run in the background even if the webpage or
  browser tab having the experiment is not currently on focus.
\end{enumerate}

>>>>

As a volunteer based system, there are some issues worth 
noting:\begin{enumerate}
\item Volunteers are anonymous, only the IP address sent in 
each request is known.
\item As anonymous entities, volunteers are not accountable. 
If a volunteer  misbehaves in some way the provider cannot 
prosecute or discipline the volunteer.
\item Participants must also trust the application provider, 
regarding invation of privacy, the integrity of their devices 
and intended application. 
\end{enumerate}

In this sense, in this paper we propose {\sf NodIO}, a cloud or metal
based 
volunteer evolutionary computing system based on the {\sf NodEO}
library, whose architecture 
has been developed using JavaScript on the client as well as the
server sides. 
All parts of the system are free and available with a free
license from \url{https://github.com/JJ/splash-volunteer}.

Thus, {\sf NodIO} architecture has two tiers:\begin{enumerate}
\item A REST server, that is, a server that includes several {\em
  routes} 
  that can be called for storing and retrieving information (the CRUD cycle:
  create, request, update and delete) from the server. The information
  is of two kinds: {\em problem} based, that is, related to the
  evolutionary algorithm such as {\tt PUT}ing a chromosome in or {\tt
    GET}ing a random chromosome from it, and {\em information} related
  to performance and state of the experiments. It also performs logging
  duties, but is basically a very lightweight and high performance
  data store \cite{jj:idc:lowcost}.
  The server has the capability to
  run a single experiment, storing the chromosomes in a data structure
  that is reset when the solution is found.
\item A client that includes the evolutionary algorithm as
  JavaScript code embedded in a web page that displays graphs and some
  additional links and information on the experiment. This code runs
  an evolutionary algorithm {\em island} starting with a random
  population and sending, every 100 generations, the best individual
  back to the server (via a {\tt PUT} request) and requesting a random
  individual from the server (via a {\tt GET} request). Apart from
  these constants, the algorithm can be run in many different ways:
  stopping when a solution is found or, as we have done in this paper,
  using Web Workers, which run in the background even if the webpage or
  browser tab having the experiment is not currently on focus.
\end{enumerate}
